Homework 1

### 2019-09-05 MSimonsHW1.tex
HW1 Prob 6 and 7

\item TODO 6

\item TODO 7

>>>>

\item First, assume $n$ is a square number.  If $n = {p_1}^{a_1} * ... * {p_k}^{a_k}$, then $\sqrt n = {p_1}^{a_1/2} * ... * {p_k}^{a_k/2}$.  By the definition of prime factorization, $a_i$ and $a_i/2$ must be integers for all $i$ such that $1 \leq i \leq k$.  Thus, $a_i/2$ can only be an integer is 2 evenly divides $a_i$.  Therefore, each $a_i$ must be even.  Next, assume each $a_i$ is even.  Let $a_i = 2b_i$ for some integers $b_i$.  Thus, $n = {p_1}^{2b_1} * ... * {p_k}^{2b_k}$.  Since each $b_i$ is an integer, $\sqrt n = {p_1}^{b_1} * ... * {p_k}^{b_k}$ is an integer and $n$ must be a square number.

\item Let $a = {p_1}^{x_1} * ... * {p_k}^{x_k}$ and $b = {q_1}^{y_1} * ... * {q_j}^{y_j}$ be the prime factorizations of $a$ and $b$ respectively such that $p_m \neq q_n$ for all $m, n$.  As such, $ab = {p_1}^{x_1} * ... * {p_k}^{x_k} * {q_1}^{y_1} * ... * {q_j}^{y_j}$.  If $ab$ is a square, then $x_1, ..., x_k$ and $y_1, ..., y_j$ must be even.  Because $x_1, ..., x_k$ are even, $a$ must a square.  Similarly, since $y_1, ..., y_j$ are even, $b$ must also be a square.
